\documentclass[12pt]{article}
\usepackage{geometry}
\geometry{letterpaper, margin=1in}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{natbib}
\bibliographystyle{apalike}


\begin{document}

\begin{center}
    {\LARGE \textbf{SITONG LI}} \\
    \small Minneapolis, MN \textbullet\ \href{mailto:ruc.sitongli@gmail.com}{ruc.sitongli@gmail.com} \textbullet\
    \href{https://www.linkedin.com/in/[YOUR-LINK]}{LinkedIn} \textbullet\
    \href{https://github.com/[YOUR-HANDLE]}{GitHub} \textbullet\ (952) 201-4026
\end{center}

\vspace{1em}

\noindent \today

\vspace{1em}

% \noindent Dear Professors Orestes, Sastry, and Wiegand,

\vspace{1em}

I am applying for the predoc position, and I am strongly committed to pursuing a Ph.D. in Economics. My research interests lie in the political economy of both democracies and non-democracies. In democratic settings such as the United States, I am interested in how political dynamics,including election cycles and populist rhetoric,shape regulators, media incentives, and firms' decisions, and in turn affect fiscal policy and economic outcomes. Prior work, including \cite{kempf2021partisan} and \cite{fos2022political}, shows that political polarization is changing financial dynamics, and \cite{cassidy2025partisan} shows that CEOs adjust their public communication accordingly. Given the broader rise of populism in many democratic countries, I see this as a timely area for research.

I am especially interested in non-democratic settings. In non-democracies like China under CCP, I want to study how information control, including censorship and propaganda, alters the information environment for markets and information intermediaries, with consequences for firms, investors, and citizens. \cite{lorentzen2014china} documents strong censorship in China, and \cite{chen2019impact} shows that censorship can discourage information seeking. Building on these insights, I am interested in how censorship changes investment behavior and market outcomes.

My motivation for these research interests is also personal, especially on the non-democracy side.I grew up and was educated in China, where politics is not something you learn from a distance, but something you live with every day. At first, I tried to find a quant job in China, and I did fixed income research at Harvest Fund. In textbooks, I was taught that being a good quant researcher means being an expert in factor mining, trading timing, or machine learning. But after I spent time researching municipal bonds, I realized I was wrong: there is no purely technical factor or theory that can substitute for understanding local fiscal capacity, policy priorities, officials' incentives, and the credibility of implicit guarantees. Basically, bond prices depend heavily on the promises and style of the highest local official; if that official is removed or investigated, policy can change and the local economic environment can shift overnight. In that setting, ``fundamentals'' cannot be separated from politics. News about leadership turnover, political campaigns, or anti-corruption investigations can be decisive, yet much of this information is censored. This was the first time I wanted to do research, and it is where my interest in non-democracies comes from.

After coming to the United States and receiving research training with Prof. Will Cassidy and Helen Zhang, I explored how senators and House members apply political pressure to the Fed Chair and how congressional information requests can shape EPA behavior.From Prof. Cassidy's project, I learned that even in a democracy---without formal censorship---political pressure on financial regulators and government agencies remains important for understanding policy and markets. These experiences are why I want to pursue research in political economy and why I am applying for this predoc.

I received most of my research training with Prof. Zhang and Prof. Cassidy, where I built and analyzed large-scale datasets and used multiple NLP tools to study topics such as political pressure and climate risk. Methodologically, I have experience with both classical NLP approaches like bag-of-words and NER and modern text-as-data methods in political economy, including MNIR \citep{taddy2013multinomial} as used in \citep{gentzkow2019measuring}, as well as state-of-the-art models such as BERT and LLM-based workflows. I am confident in my coding skills, and I am equally careful about how to present text-based measures in a paper, with a clear understanding of how measurement error can enter at each step. With the emergence of LLMs, measurement from text and other alternative data has become easier, but measurement error can also become larger if workflows are not transparent and reproducible. I pay particular attention to practical steps that reduce noise and improve robustness, for example, controlling temperature, using cross-validation, and checking results with alternative NLP specifications. I also read widely in the textual analysis literature and discuss methods with authors to understand not only how they control error, but also how they communicate these choices to editors and discussants. For example, \citep{hampole2025artificial} use a local LLM to improve robustness, and I suggested adding similar robustness checks to our project.

As a predoctoral researcher, I would aim to contribute in three ways. First, I can build and maintain scalable data pipelines for large dataset. Second, I can develop measurement strategies for narratives and information control using NLP/LLMs if you want to add textual analysis in your research, while paying careful attention to robustness and interpretability. Third, I can support credible empirical designs—setting up clean panels, implementing event-study or difference-in-differences frameworks, and producing transparent replication-ready code.

I would be grateful for the opportunity to work with your group and deepen my training in economy research. I am confident that my background—combining lived intuition about non-democratic institutions, substantive interest in censorship and propaganda, and strong technical skills in data and text analysis—would allow me to contribute meaningfully to your research agenda.

\vspace{1em}

\noindent Sincerely,\\
\vspace{0.5em}
\textbf{Sitong Li}
\bibliography{refs}
\end{document}
